Textual Features

### 2017-08-03 Hours.Rmd
started fitting CR model, reorganized/added to files, updated hours

>>>>

7/31/2017 | 2 | 10:00-12:00PM | Organized stuff, started thinking about the model 
7/31/2017 | 2 | 3:00-5:00PM | Text mining and wordclouds on iPhone and Android Phone subcategories 
8/1/2017 | 3.5 | 12:00-3:30PM | Started the process of fitting the model 
8/1/2017 | 3 | 5:30-8:30PM | Organized/added to files
8/2/2017 | 5 | 1:15-6:15PM | Fitted CR models, changes summary_stats files..

### 2017-08-03 freq_words.Rmd
started fitting CR model, reorganized/added to files, updated hours

#function to clean corpus
clean_corpus <- function(corpus){
  library(tm)
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n is an optional argument 
freq_terms <- function(vec, n = NULL) {
  library(qdap)
  library(tm)
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  freq_df <- data.frame(word = names(freq), frequency = unname(freq))

  if (is.null(n)) {
    return(freq_df)
  }
  else if (!is.null(n)) {
    return(freq_df[1:n,])
  }
}

@@

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

@@

ggplot(titles_freq, aes(x = frequency)) + 
  geom_histogram() + 
  ggtitle("Distribution of word frequencies")
```

```{r, echo = FALSE}
top50 <- titles_freq[1:50,]
top50$word <- factor(top50$word, levels = top50$word)

ggplot(top50, aes(x = word, y = frequency/nrow(x))) + 
  geom_point() +
  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("How often the 50 most frequently used words appear")
```

@@

```{r, echo = FALSE}
x %>%
  group_by(contain_top10) %>%
  summarise(median_time = median(time_until_answer), 
            avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
survdiff(surv_object~contain_top10, data = x)
```

```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
KM_top10 <- survfit(surv_object ~ contain_top10, data = x)
plot_surv(KM_top10, data = x)
```

@@

##### median answer time and average daily views grouped by whether or not question contains at least 1 uanswered term

```{r, echo = FALSE}
x %>%
  group_by(contain_u) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u, data = x)
```

```{r, echo = FALSE}
KM_u <- survfit(surv_object ~ contain_u, data = x) 
plot_surv(KM_u, data = x)
```

@@

##### median answer time and average daily views grouped by whether or not question contains at least 1 answered term

```{r, echo = FALSE}
x %>%
  group_by(contain_a) %>%
  summarise(median_time = median(time_until_answer), n = n(), avg_views = mean(daily_views)) %>%
  arrange(median_time)
```

@@

```{r, echo = FALSE}
survdiff(surv_object~contain_a, data = x)
```

```{r, echo = FALSE}
KM_a <- survfit(surv_object ~ contain_a, data = x)
plot_surv(KM_a, data = x)
```

>>>>

#function to clean corpus
clean_corpus <- function(corpus){
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, content_transformer(tolower))
  corpus <- tm_map(corpus, removeWords, c(stopwords("en"), "can", "will", "cant", "wont", "works", "get", "help", "need"))
  return(corpus)
}

#function that takes in character vector and returns a data frame of words and frequencies sorted by most to least frequent, n is an optional argument 
freq_terms <- function(vec, n = NULL) {
  source <- VectorSource(vec)
  corpus <- VCorpus(source)
  cleaned_corpus <- clean_corpus(corpus) 
  dtm <- DocumentTermMatrix(cleaned_corpus)
  m <- as.matrix(dtm) 
  freq <- colSums(m)
  freq <- sort(freq, decreasing = TRUE)
  freq_df <- data.frame(word = names(freq), frequency = unname(freq))

  if (missing(n)) {
    return(freq_df)
  }
  else {
    return(freq_df[1:n,])
  }
}

@@

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}

#produces summary stats grouped by variable 
sum_stats <- function(variable, data) {
  tbl <- x %>%
    group_by(data[[variable]]) %>%
    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
    arrange(median_time)
  names(tbl)[1] <- variable
  return(tbl)
}
```

@@

ggplot(titles_freq, aes(x = frequency)) + 
  geom_histogram() + 
  ggtitle("Distribution of word frequencies")

top50 <- titles_freq[1:50,]
top50$word <- factor(top50$word, levels = top50$word)

library(forcats)

ggplot(top50, aes(x = fct_reorder(word, -frequency), y = frequency/nrow(x))) + 
  geom_point() +
  scale_y_continuous("Percentage of times the word appears", labels = scales::percent) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("How often the 50 most frequently used words appear")
```

@@

```{r, echo = FALSE}
sum_stats("contain_top10", data = x)
```

@@

```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")
survdiff(surv_object~contain_top10, data = x)

KM_top10 <- survfit(surv_object ~ contain_top10, data = x)
plot_surv(KM_top10, data = x)
```

@@

##### summary stats for contain_u

```{r, echo = FALSE}
sum_stats("contain_u", data = x)
```

@@

```{r, echo = FALSE}
survdiff(surv_object ~ contain_u, data = x)
KM_u <- survfit(surv_object ~ contain_u, data = x) 
plot_surv(KM_u, data = x)
```

@@

##### summary stats for contain_a

```{r, echo = FALSE}
sum_stats("contain_a", data = x)
```

@@

```{r, echo = FALSE}
survdiff(surv_object~contain_a, data = x)
KM_a <- survfit(surv_object ~ contain_a, data = x)
plot_surv(KM_a, data = x)
```

### 2017-08-03 summary_stats.Rmd
started fitting CR model, reorganized/added to files, updated hours

#### About the data set:

@@

#### Exploring the response: time_until_answer

@@

* **minimum:** `r round(min(x$time_until_answer), 2)` hrs
* **maximum:** `r round(max(x$time_until_answer), 2)` hrs, `r round(max(x$time_until_answer)/24, 2)` days
* **mean:** `r round(mean(x$time_until_answer), 2)` hrs, `r round(mean(x$time_until_answer)/24, 2)` days
* **median:** `r round(median(x$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)`hrs
* **third quartile:** `r round(summary[5], 2)` hrs, `r round(summary[5]/24, 2)` days
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs, `r round((summary[5] - summary[2])/24, 2)` days
* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions had been answered
* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions had been answered

```{r, echo = FALSE}
ggplot(x, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous("Time (hours)") +
  ggtitle("Distribution of time_until_answer values")
```

@@

##### Survival Time Statistics based off of KM Estimator 
```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")

@@

s <- summary(KM)
round(s$table, 2)
```

* **Min survival probability:** `r round(min(s$surv), 2)`
* **Max survival probability:** `r round(max(s$surv), 2)`
* **rmean survival time:** `r round(s$table[5], 2)` hrs, `r round(s$table[5]/24, 2)` days
* **SE of rmean:** `r round(s$table[6], 2)` hrs
* **Median survival time:** `r round(s$table[7], 2)` hrs
* **95% confidence interval for the median:** (`r round(s$table[8], 2)`,`r round(s$table[9], 2)`)

@@

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.64, 0.75))
round(quant[[1]], 3)
```
* **Interpretations:**
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
    + highest quantile that exists: `r round(quant$quantile[6], 2)` hrs 64% of the questions have been answered

@@

* Survival curve shows that survival probability drops immediately after question is posted. Within a few hours after posting, survival probability levels out, hovers around 0.35 (never hits 0).

```{r, survival curves, echo = FALSE}
ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", main = "KM Curve")
ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", main = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
```

@@

* at 100 hrs, the probability that a question is answered starts to level out at around ~0.63

```{r, echo = FALSE}
reversed <- data.frame(time = s$time, prob_ans = 1-s$surv)
ggplot(reversed, aes(x = time, y = prob_ans)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)", limits = c(0,100)) + 
  scale_y_continuous("Probability a question is answered") + 
  ggtitle("Probability a question is answered vs. time (hours)")
```

### Instantaneous Hazard Rates (based off of KM estimates)

@@

* **Max instant hazard rate:** `r round(max(h.hat$est), 2)` at time: `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
* **Min instant hazard rate:** `r round(min(h.hat$est), 2)`

@@

### Cumulative Hazard Rates

>>>>

### About the data set:

@@

### Exploring the response: time_until_answer

@@

* **minimum:** `r round(min(x$time_until_answer), 2)` hrs
* **maximum:** `r round(max(x$time_until_answer), 2)` hrs (`r round(max(x$time_until_answer)/24, 2)` days)
* **mean:** `r round(mean(x$time_until_answer), 2)` hrs (`r round(mean(x$time_until_answer)/24, 2)` days)
* **median:** `r round(median(x$time_until_answer), 2)` hrs
* **first quartile:** `r round(summary[2], 2)`hrs
* **third quartile:** `r round(summary[5], 2)` hrs (`r round(summary[5]/24, 2)` days)
* **IQR range:** `r round(summary[5] - summary[2], 2)` hrs (`r round((summary[5] - summary[2])/24, 2)` days)
* Within an hour, `r round((sum(x$time_until_answer <= 1)/nrow(x))*100,2)`% of the questions have been answered
* Within 5 hours, `r round((sum(x$time_until_answer <= 5)/nrow(x))*100,2)`% of the questions have been answered

```{r, echo = FALSE}
ggplot(x, aes(x = time_until_answer)) + 
  geom_histogram(bins = 10) + 
  scale_x_continuous("Time (hours)") +
  ggtitle("Distribution of answer times")
```

@@

##### Based off of the Kaplan-Meier Estimator 
```{r, echo = FALSE}
surv_object <- Surv(x$time_until_answer, x$answered, type = "right")

@@

s <- summary(KM)
```

* number of complete events/answered questions: `r s$table[4]` (`r nrow(x)` total questions) 
* smallest survival probability: `r round(min(s$surv), 2)`
* largest survival probability: `r round(max(s$surv), 2)`
* mean survival time: `r round(s$table[5], 2)` hrs (`r round(s$table[5]/24, 2)` days)
* SE of the mean: `r round(s$table[6], 2)` hrs
* Median survival time: `r round(s$table[7], 2)` hrs
* 95% confidence interval for the median: (`r round(s$table[8], 2)` hrs,`r round(s$table[9], 2)` hrs)

@@

```{r, percentiles, echo = FALSE}
quant <- quantile(KM, c(0.01, 0.10, 0.25, 0.30, 0.50, 0.64, 0.75))
round(quant[[1]], 3)
```
* Interpretations:
    + By `r round(quant$quantile[1], 2)` hrs 1% of the questions have been answered
    + By `r round(quant$quantile[2], 2)` hrs 10% of the questions have been answered
    + By `r round(quant$quantile[3], 2)` hrs 25% of the questions have been answered
    + By `r round(quant$quantile[4], 2)` hrs 30% of the questions have been answered
    + By `r round(quant$quantile[5], 2)` hrs 50% of the questions have been answered
    + 75th percentile doesn't exist (lowest survival probability: `r round(min(summary(KM)$surv),2)`)
    + highest quantile that exists: By `r round(quant$quantile[6], 2)` hrs (`r round(quant$quantile[6]/24, 2)` days) 64% of the questions have been answered

@@

* Survival curve shows that survival probability drops immediately after question is posted. 
* Within a few hours after posting, the survival probability levels out (though it still decreases at a slow rate), and hovers around 0.35 (never hits 0).

```{r, survival curves, echo = FALSE}
ggsurvplot(KM, data = x, risk.table = TRUE, xlab = "Time (hours)", title = "KM Curve")
```

```{r, echo = FALSE}
ggsurvplot(KM, data = x, risk.table = FALSE, xlab = "Time (hours)", title = "KM Curve (zoomed in)", xlim = c(0,50), break.x.by = 10)
```

@@

* At around 100 hours, the probability a question is answered before time t starts to level out at around ~0.63

```{r, echo = FALSE}
reversed <- data.frame(time = s$time, prob_ans = 1-s$surv)
ggplot(reversed, aes(x = time, y = prob_ans)) + 
  geom_line() + 
  scale_x_continuous("Time (hours)", limits = c(0,100)) + 
  scale_y_continuous("Probability a question is answered before time t") + 
  ggtitle("Probability a question is answered before a certain time vs. time (hours)")
```

##### Instantaneous Hazard Rates (based off of KM estimates)

@@

* Max instant hazard rate: `r round(max(h.hat$est), 2)` at `r round(h.hat$time[which(h.hat$est == max(h.hat$est))], 2)` hrs 
* Min instant hazard rate: `r round(min(h.hat$est), 2)`
* Interpretations: 
    +

@@

##### Cumulative Hazard Rates

### 2017-08-03 tag_exploration.Rmd
started fitting CR model, reorganized/added to files, updated hours

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

```{r, echo = FALSE}
#matrix of tags (splitting up tags variable wherever there's a comma)
split_tags <- str_split(x$tags, ", ", simplify = TRUE)

@@

### avg_tag_length

* average length of tag for a question: total number of characters for all of a question's tags / number of tags the question has
* think that tags that are more concise (fewer characters) will have faster answer times

```{r, echo = FALSE}
#average tag length: 
x$avg_tag_length <- NA
not_na <- which(x$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  x$avg_tag_length[i] <- total_char / total_tags
}

ggplot(x, aes(x = avg_tag_length)) + 
  geom_histogram() + 
  scale_x_continuous("Average tag length for each question (characters)") + 
  ggtitle("Distribution of average tag lengths")

@@

* longest average tag length: `r max_avg`
* shortest average tag length: `r min_avg`
* mean average tag length: `r mean_length`
* median average tag length: `r median_length`

##### average tag length grouped by product category 
```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(avg_length = mean(avg_tag_length, na.rm = TRUE), median_length = median(avg_tag_length, na.rm = TRUE), n = n(), avg_views = mean(daily_views), median_time = median(time_until_answer)) %>%
  arrange(avg_length)
```

##### average tag length grouped by answered/unanswered questions
```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(avg_tag_length, na.rm = TRUE))
```

### frequency of tags (popularity)

@@

ggplot(tag_freq, aes(x = percent)) + 
  geom_histogram() + 
  ggtitle("Distribution of tag frequency")

top50 <- tag_freq[1:50,]
ggplot(top50, aes(x = fct_reorder(tag, -percent), y = percent)) + 
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  ggtitle("Distribution of top 50 tags and percentage of times they occur")
```

```{r, echo = FALSE}
#creating average frequency/popular score variable
x$tag1 <- split_tags[,1]
x$tag2 <- split_tags[,2]
x$tag3 <- split_tags[,3]
x$tag4 <- split_tags[,4]

@@

ggplot(x, aes(x = avg_score)) + 
  geom_histogram() + 
  ggtitle("Distribution of average tag popularity/frequency scores")
```

#### Determining threshold for popular/unpopular tags

```{r, echo = FALSE}
median_score <- median(x$avg_score)
q_score <- quantile(x$avg_score, probs = seq(0, 1, by = 0.25))
percentile80 <- quantile(x$avg_score, probs = 0.80)

x$popular_tag <- FALSE
x$popular_tag[x$avg_score >= percentile80] <- TRUE

prop_popular <- sum(x$popular_tag)/sum(x$n_tags != 0)
```

* median average popularity/frequency score: `r median_score` 
* 75th percentile for scores: `r q_score[4]`
* popularity threshold based off of 80th percentile: `r percentile80`
* proportion of questions that contain a tag that are "popular": `r prop_popular`

##### Log-rank test

@@

### incorrect use of tags
* correct tags
    + don't begin with "#"
    + have no more than 3 words (?)
    + no spelling errors (ex: troubleshoot espressomaschine)
    + no punctuation marks (ex: !, ?, "", /) - since there are tags like: macbook pro 15", just one " is fine
    + should not end with a "."
    + doesn't contain links
    + if it contains numbers must also contain letters 
* regex
* look at probability a quesiton includes certain tag- chances it's answered (grab most frequent)
* maybe ignore tags that are also in device names

```{r, echo = FALSE}
x$correct_tag <- NA_character_
x$correct_tag[x$n_tags != 0] <- TRUE

@@

##### Log-rank test

@@

### If a question contains top50 tags

```{r, echo = FALSE}
top50tag <- as.character(top50$tag)

@@

##### median time, prop answered and average daily views grouped by whether or not it contains a top50 tag
```{r, echo = FALSE}
x %>% 
  group_by(contain_toptag) %>%
  summarise(median_time = median(time_until_answer), avg_views = mean(daily_views), n = n(), prop_answered = sum(answered)/n)
```

##### log-rank test 
```{r, echo = FALSE}
survdiff(surv_object ~ contain_toptag, data = x)
KM_toptag <- survfit(surv_object ~ contain_toptag, data = x)
plot_surv(KM_toptag, data = x)
```

### maximum number of words in a tag

```{r, echo = FALSE}
x$max_tagwords <- rep(NA, nrow(x))
for (i in which(x$n_tags != 0)) {
  tags <- as.vector(split_tags[i,])
  x$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
}

>>>>

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}

sum_stats <- function(variable, data) {
  tbl <- x %>%
    group_by(data[[variable]]) %>%
    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
    arrange(median_time)
  names(tbl)[1] <- variable
  return(tbl)
}
```

```{r, include = FALSE}
#matrix of tags (splitting up tags variable wherever there's a comma)
split_tags <- str_split(x$tags, ", ", simplify = TRUE)

@@

### Average Tag Length

```{r, include = FALSE}
x$avg_tag_length <- NA
not_na <- which(x$tags != "")
for (i in not_na) {
  total_char <- sum(str_length(as.vector(split_tags[i,])))
  total_tags <- sum(as.vector(split_tags[i,]) != "")
  x$avg_tag_length[i] <- total_char / total_tags
}

@@

* average length of tag for a question: total number of characters for all of a question's tags / number of tags the question has
* hypothesis: questions with longer average tag lengths will have slower answer times (tags that are concise and include only a word will have faster answer times)
* **longest average tag length:** `r max_avg`
* **shortest average tag length:** `r min_avg`
* **mean average tag length:** `r mean_length`
* **median average tag length:** `r median_length`

```{r, echo = FALSE}
ggplot(x, aes(x = avg_tag_length)) + 
  geom_histogram() + 
  scale_x_continuous("Average tag length for each question (characters)") + 
  ggtitle("Distribution of average tag lengths")
```

##### Average tag length grouped by category

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(n = n(), median_views = median(daily_views), median_time = median(time_until_answer), avg_length = mean(avg_tag_length, na.rm = TRUE)) %>%
  arrange(avg_length)
```

##### Average tag length grouped by answered

```{r, echo = FALSE}
x %>%
  group_by(as.factor(answered)) %>%
  summarise(avg_length = mean(avg_tag_length, na.rm = TRUE))
```

### Maximum number of words in a tag

* Another way to capture if the length of a tag is too long? 
* Will show if a question contains a really long tag- indicates incorrect tagging

```{r, echo = FALSE}
x$max_tagwords <- rep(0, nrow(x))
for (i in which(x$n_tags != 0)) {
  tags <- as.vector(split_tags[i,])
  x$max_tagwords[i] <- max(str_count(tags, pattern = "\\w+"))
}

##### log-rank test (for each level of maximum words)

```{r, echo = FALSE}
survdiff(surv_object ~ as.factor(max_tagwords), data = x)
KM_maxwords <- survfit(surv_object ~ as.factor(max_tagwords), data = x)
plot_surv(KM_maxwords, data = x)
```

### Frequency of tags (popularity?)

* Took the unique tags, counted the number of times each tag occured in the data, and calculated the proportion of times it appeared = frequency of the tag 
* Average frequency score for a question: average frequency score for each tag in a question

##### First 6 of the tags that appear the most

@@

head(tag_freq)

library(forcats)

top50 <- tag_freq[1:50,]
ggplot(top50, aes(x = fct_reorder(tag, -percent), y = percent)) + 
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  scale_y_continuous(labels = scales::percent) + 
  ggtitle("Distribution of the top 50 tags and percentage of times they occur in the data")
```

```{r, echo = FALSE}
#creating average frequency score variable
x$tag1 <- split_tags[,1]
x$tag2 <- split_tags[,2]
x$tag3 <- split_tags[,3]
x$tag4 <- split_tags[,4]

@@

ggplot(x, aes(x = avg_score)) + 
  geom_histogram() + 
  ggtitle("Distribution of average tag frequency scores for each question")
```

##### Determining the threshold for what's considered frequent/unfrequent tags

```{r, include = FALSE}
median_score <- median(x$avg_score)
q_score <- quantile(x$avg_score, probs = seq(0, 1, by = 0.25))
percentile80 <- quantile(x$avg_score, probs = 0.80)

x$frequent_tag <- FALSE
x$frequent_tag[x$avg_score >= percentile80] <- TRUE

prop_frequent <- sum(x$frequent_tag)/sum(x$n_tags != 0)
```

* median average popularity/frequency score: `r median_score` 
* 75th percentile for scores: `r q_score[4]`
* **popularity threshold based off of 80th percentile:** `r percentile80`
* proportion of questions that contain a tag that are "popular": `r prop_frequent`

##### Log-rank test (for frequent/unfrequent tags)

@@

### Incorrect use of tags
* correct tags
    + don't begin with "#"
    + have no more than 3 words (?)
    + no spelling errors (ex: troubleshoot espressomaschine)
    + no punctuation marks (ex: !, ?, "", /) - since there are tags like: macbook pro 15", just one " is fine
    + should not end with a "."
    + doesn't contain links
    + if it contains numbers must also contain letters 
* look at probability a question is answered if it contain's a certain tag
* maybe ignore tags that are also in device names

```{r, include = FALSE}
x$correct_tag <- NA_character_
x$correct_tag[x$n_tags != 0] <- TRUE

@@

##### Log-rank test (for incorrect vs correctly tagged questions)

@@

### If a question contains at least one of the top 50 most frequent tags

```{r, include = FALSE}
top50tag <- as.character(top50$tag)

@@

##### Summary stats grouped by contain_toptag
```{r, echo = FALSE}
sum_stats("contain_toptag", data = x)
```

##### log-rank test (for questions that contain vs don't contain)
```{r, echo = FALSE}
survdiff(surv_object ~ contain_toptag, data = x)
KM_toptag <- survfit(surv_object ~ contain_toptag, data = x)
plot_surv(KM_toptag, data = x)
```

### 2017-08-03 textual_analysis.Rmd
started fitting CR model, reorganized/added to files, updated hours

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}
```

@@

```{r, echo = FALSE}
x$first_punct <- str_locate(x$text, pattern = "[.|,|?|!|;|:]")[,1]

@@

##### Average and median first_punc grouped by answered

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(avg_pos = mean(first_punct, na.rm = TRUE), median_pos = median(first_punct, na.rm = TRUE), n = n())
```

##### Average and median first_punct grouped by category

@@

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(avg_pos = mean(first_punct, na.rm = TRUE), median_pos = median(first_punct, na.rm = TRUE), n = n()) %>%
  arrange(median_pos)
```

@@

##### Median time_until_answer grouped by whether or not text contains punct

@@

x %>%
  group_by(contain_punct) %>%
  summarise(median_time = median(time_until_answer), n = n())
```

##### Proportion of answered/unanswered questions that contain punct

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_contain = sum(contain_punct)/n)
```

##### Proportion that contain punct grouped by categories

@@

##### Median time_until_answer grouped by whether or not text ends with punct

```{r, echo = FALSE}
x %>% 
  group_by(end_punct) %>%
  summarise(median_time = median(time_until_answer), n = n())
```

##### Proportion of answered/unanswered questions that end with punct

```{r, echo = FALSE}
x %>% 
  group_by(answered) %>%
  summarise(n = n(), prop_end = sum(end_punct)/n)
```

@@

```{r, question mark, echo = FALSE}
x$contain_question <- str_detect(x$title, pattern = QUESTION)

@@

##### median time grouped by whether or not title contains: '?'

```{r, echo = FALSE}
x %>%
  group_by(contain_question) %>%
  summarise(median_time = median(time_until_answer), n = n()) %>%
  arrange(median_time)
```

@@

##### median time and proportion answered grouped by begin_wh
```{r, echo = FALSE}
x %>%
  group_by(begin_wh) %>%
  summarise(median_time = median(time_until_answer), n = n(), prop_answered = sum(answered)/n)
```

##### log-rank test
```{r, echo = FALSE}
survdiff(surv_object ~ begin_wh, data = x)
KM_wh <- survfit(surv_object ~ begin_wh, data = x)
plot_surv(KM_wh, data = x)
```

@@

### If first letter of text is capitalized
```{r, echo = FALSE}
x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")

@@

##### Proportion in answered/unanswered questions with capital letter in text
```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_capital = sum(capital_text)/n)
```

@@

##### Proportion all lower case grouped by answered/unanswered

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_allLower = sum(all_lower)/n)
```

@@

##### median time/average daily views grouped by whether or not question contains "tried"/"searched"
```{r, echo = FALSE}
x %>%
  group_by(prior_effort) %>%
  summarise(median_time = median(time_until_answer), avg_daily = mean(daily_views), n = n()) %>%
  arrange(median_time)
```

##### proportion within answered/unanswered questions that indicate prior effort

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(n = n(), prop_indicateeffort = sum(prior_effort)/n) 
```

@@

##### Median time grouped by whether or not gratitude is expressed

```{r, echo = FALSE}
x %>%
  group_by(gratitude) %>%
  summarise(median_time = median(time_until_answer))
```

##### proportion in answered/unanswered questions that express gratitude

```{r, echo = FALSE}
x %>% 
  group_by(answered) %>%
  summarise(n = n(), prop_gratitude = sum(gratitude)/n)
```

@@

### Does greeting people matter? (presence of "hi")

@@

@@

>>>>

      if ("strata" %in% names(df)) {
        ggplot(df, aes(x = time, y = surv, color = strata)) + 
          geom_line() + 
          scale_y_continuous("Survival Probabilities") +
          scale_x_continuous("Time (hours)", limits = xlim) + 
          ggtitle("Survival Curves") + 
          geom_dl(aes(label = strata), method = list(dl.trans(x = x + 0.2), "last.points", cex = 0.5))
      }
  }
}

#function that prints out summary stats grouped by that variable 
sum_stats <- function(variable, data) {
  tbl <- x %>%
    group_by(data[[variable]]) %>%
    summarise(n = n(), median_time = median(time_until_answer), median_views = median(daily_views), prop_answered = sum(answered)/n) %>%
    arrange(median_time)
  names(tbl)[1] <- variable
  return(tbl)
}
```

@@

* search for : ; , ? or limit the search to just end punctuation?

```{r, echo = FALSE}
x$first_punct <- str_locate(x$text, pattern = "[.|?|!]")[,1]

@@

##### Median first_punc grouped by answered

```{r, echo = FALSE}
x %>%
  group_by(answered) %>%
  summarise(median_pos = median(first_punct, na.rm = TRUE), n = n())
```

##### Median first_punct and time grouped by category

@@

```{r, echo = FALSE}
x %>%
  group_by(category) %>%
  summarise(median_pos = median(first_punct, na.rm = TRUE), n = n(), median_time = median(time_until_answer)) %>%
  arrange(desc(median_pos))
```

@@

##### summary stats grouped by contain_punct

@@

sum_stats("contain_punct", data = x)
```

##### Proportion that contain any punctuation grouped by categories

@@

##### summary stats for end_punct

```{r, echo = FALSE}
sum_stats("end_punct", data = x)
```

@@

```{r, question mark, echo = FALSE}
x$contain_question <- str_detect(x$title, pattern = QUESTION %R% END)

@@

##### summary stats for contain_question

```{r, echo = FALSE}
sum_stats("contain_question", data = x)
```

@@

##### summary stats for begin_wh

```{r, echo = FALSE}
sum_stats("begin_wh", data = x)
```

```{r, echo = FALSE}
survdiff(surv_object ~ begin_wh, data = x)
KM_wh <- survfit(surv_object ~ begin_wh, data = x)
plot_surv(KM_wh, data = x)
```

@@

### If first letter of text is capitalized

```{r, echo = FALSE}
x$capital_text <- str_detect(x$text, pattern = "^[[:upper:]]")

@@

##### Proportion in answered/unanswered questions with capital letter in text
```{r, echo = FALSE}
sum_stats("capital_text", data = x)
```

@@

##### summary stats for all_lower

```{r, echo = FALSE}
sum_stats("all_lower", data = x)
```

@@

##### summary stats for prior_effort

```{r, echo = FALSE}
sum_stats("prior_effort", data = x)
```

@@

##### summary stats for gratitude

```{r, echo = FALSE}
sum_stats("gratitude", data = x)
```

##### New and continuing users and expressing gratitude

```{r, echo = FALSE}
x %>% 
  group_by(new_user) %>%
  summarise(n = n(), prop_gratitude = sum(gratitude)/n)
```

@@

### Does greeting people matter? (presence of ex: "hi")

@@

##### summary stats grouped by greeting

```{r, echo = FALSE}
sum_stats("greeting", data = x)
```

##### New and continuing users and greetings 
```{r, echo = FALSE}
x %>%
  group_by(greeting) %>%
  summarise(n = n(), prop_new = sum(new_user)/n)
```

@@

### If the asker updated the question

```{r, echo = FALSE}
x$update <- str_detect(x$text, pattern = "===")

prop_update <- sum(x$update)/nrow(x)
```

* `r round(prop_update*100,2)`% of users updated their question after posting it

##### summary statitics grouped by update

```{r, echo = FALSE}
sum_stats("update", data = x)
```

##### proportion of new/continuing users that updated their question

```{r, echo = FALSE}
x %>%
  group_by(new_user) %>%
  summarise(n = n(), prop_update = sum(update)/n)
```

```{r, echo = FALSE}
survdiff(surv_object ~ update, data = x)
KM_update <- survfit(surv_object ~ update, data = x)
plot_surv(KM_update, data = x)
```
